\documentclass[12pt]{article}
\pagestyle{empty}

\usepackage{graphicx}
\usepackage{amsmath}

\setlength\oddsidemargin{-0.5in}
\setlength\evensidemargin{-0.5in}
\setlength\textwidth{7in}
\setlength\textheight{10in}
\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0in}

\newcommand{\up}{$~$\vspace*{-0.7in}}
\newcommand{\ans}{\noindent Ans.\underline{\hspace{3in}}}
\newcommand{\liner}{\noindent\underline{\hspace*{7in}}}
\newcommand{\spac}{\hspace*{3em}}
\newcommand{\ds}{\displaystyle}
\newcommand{\halfspac}{\hspace*{1.5em}}

\begin{document}

\up

{\bf Ch 13 Study Guide  \hspace*{1em} Your Name: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \hspace*{1em} Class: 9am / 1pm}

\vspace*{0.2in}

\centerline{ \bf Calculus III - Math 2630 - Fall 2012 \spac Instructor: Steven Clontz}

\vspace*{0.2in}

{\bf Draw a \framebox{box} around your answer. Show your work. Pens/calculators not allowed.}

\indent\liner


\begin{enumerate}

% (13.2) Nonrectangular Double Integral

\item Evaluate $\ds \int_{1}^{2}\int_{1/x}^{2/x} xe^x \,dy\,dx$.

  \begin{itemize}
  \item Correctly integrate inside function (4 pts)
  \item Correctly evaulate inside integral (3 pts)
  \item Correctly evaulate outside integral (3 pts)
  \end{itemize}

\vspace*{6in}

\liner

\newpage\up

% (13.2) Reversing order of integration of nonrectangular double integral.

\item Evaluate $\ds \int_{0}^{1}\int_{\sqrt{y}}^{1} \frac{3}{1+x^3}\,dx\,dy$.

  \begin{itemize}
  \item Draw region of integration correctly (3 pts)
  \item Set up new bounds of integration correctly (4 pts)
  \item Correctly evaulate new double iterated integral (3 pts)
  \end{itemize}

\vspace*{8in}

\liner

\newpage\up

% (13.3) Area by Double Integration

\item Express the area of the region between the curves $y=4-x^2$ and $y=x^2-4$ as a double iterated integral. \textbf{Do not evaluate the integral.}

  \begin{itemize}
  \item Use correct formula $A = \iint_{R}\,dA$ (3 pts)
  \item Draw region of integration correctly (3 pts)
  \item Set up bounds of integration correctly (3 pts)
  \item Write correct double iterated integral (1 pt)
  \end{itemize}

\vspace*{7.5in}

\liner

\newpage\up

% (13.3) Average Value of a two-variable function

\item Express the average value of the function $f(x,y)=3xy^2$ over the triangle with sides given by the lines $x=4$, $y=0$, $x=2y$ as a multiple of a double iterated integral. \textbf{Do not evaluate the integral.}

  \begin{itemize}
  \item Use correct formula $\frac{1}{\text{area of }R}\iint_{R}f(x,y)\,dA$ (3 pts)
  \item Find area of the triangular/rectangular region (2 pts)
  \item Set up bounds of integration correctly (3 pts)
  \item Write correct multiple of double iterated integral (2 pts)
  \end{itemize}

\vspace*{7in}

\liner

\newpage\up

% (13.5) Evaluate a triple nonrectangular integral

\item Evaluate $\ds \int_{0}^{1}\int_0^{z}\int_0^{x+z} 36xz \,dy\,dx\,dz$.

  \begin{itemize}
  \item Evaulate inner integral correctly (4 pts)
  \item Evaulate inner \& middle integrals correctly (3 pts)
  \item Evaulte entire triple iterated integral correctly (3 pts)
  \end{itemize}

\vspace*{8in}

\liner

\newpage\up

% (13.5) Volume of 3D Region

\item Express the volume of the region in $xyz$ space in the first octant bounded by  the coordinate planes and the plane $x+3y+2z=6$ as a triple iterated integral. \textbf{Do not evaluate the integral.}

  \begin{itemize}
  \item Set up integral of the form $\int_{\text{constant}}^{\text{constant}}\int_{\leq 1\text{ var}}^{\leq 1\text{ var}}\int_{\leq 2\text{ var}}^{\leq 2\text{ var}} \, dV$ (4 pts)
  \item Set up innermost bounds correctly (3 pts)
  \item Set up all bounds correctly (3 pts)
  \end{itemize}

\vspace*{8in}

\liner

\newpage\up

% (13.8) Finding 2D Transformation

\item Find a transformation $x(u,v)$, $y(u,v)$ from the triangle with coordinates $(0,0)$, $(1,0)$, and $(1,1)$ in the $uv$ plane into the triangle with vertices $(0,0)$, $(2,2)$, and $(1,4)$ in the $xy$ plane.

  \begin{itemize}
  \item Draw picture of regions in $uv$ and $xy$ planes (2 pts)
  \item Label sides of regions in both planes correctly (3 pts)
  \item Relate sides of regions in both planes correctly (3 pts)
  \item Solve the system of equations for the correct transformation (2 pts)
  \end{itemize}

\vspace*{7in}

\liner

\newpage\up

% (13.8) 2D Substitution

\item Using the transformation $x=3u-2v$, $y=2u+4v$ from the unit square in the $uv$ plane into the parallelogram $R$ with vertices $(0,0)$, $(3,2)$, $(1,6)$, and $(-2,4)$ in the $xy$ plane, evaulate \[\iint\limits_{R} \left(2x-y\right) \,dx\,dy\]

  \begin{itemize}
  \item Substitute $x(u,v)$, $y(u,v)$ for $x$, $y$ (2 pts)
  \item Evaulate the Jacobian correctly, multiply the entire function by its absolute value (3 pts)
  \item Set up the correct new bounds of integration (2 pts)
  \item Evaulate the integral correctly (3 pts)
  \end{itemize}

\vspace*{7in}

\liner

\newpage\up

% (13.4) Changing Cartesian to Polar Integral

\item Evaluate $\ds\int_{0}^2\int_0^{\sqrt{4-x^2}} 3\sqrt{x^2+y^2}\,dy\,dx$.

  \begin{itemize}
  \item Draw the region of integration correctly (3 pts)
  \item Set up new polar bounds of integration (3 pts)
  \item Replace $x,y$ with $r\cos\theta,r\sin\theta$ and replace $dA$ with $r\,dr\,d\theta$ (2 pts)
  \item Evaulate the integral correctly (2 pts)
  \end{itemize}

\vspace*{7.6in}

\liner

\newpage

% (13.7) Changing Cartesian to Spherical Integral

\item Express the volume of the solid inside the sphere $x^2+y^2+z^2=4$ ($\rho=2$) and above the cone $z=\frac{\sqrt{3}}{2}\sqrt{x^2+y^2}$ ($\phi=\pi/6$) as a triple iterated integral using spherical coordinates. \textbf{Do not evaluate the integral.}

  \begin{itemize}
  \item Use volume formula $\iiint_D \,dV$ (3 pts)
  \item Set up spherical bounds of integration (4 pts)
  \item Replace $dV$ with $\rho^2\sin\phi\,d\rho\,d\phi\,d\theta$ (3 pts)
  \end{itemize}

\vspace*{7in}

\liner

\newpage

%% Two pages of scratch work! %%
\centerline{Include extra scratch work below:}
\liner
\newpage
\centerline{Include extra scratch work below:}
\liner

\end{enumerate}

\end{document}
